---
title: "Untitled"
output: 
  powerpoint_presentation:
    toc: true
    toc_depth: 3
date: '2023-01-24'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slides structure

---

Slide with no header

---
:::::: {.columns}
::: {.column}
Content of the left column.
:::

::: {.column}
Content of the right column.
:::
::::::

## Tabset structure {.tabset}

### By Product

(tab content)

### By Region

(tab content)
